% limitations.tex
% Drop-in limitations section for IPIBench paper.
% Include with: \input{limitations}  (before \section{Conclusion})
%
% One placeholder to fill in before submission:
%   [X]  — manual/automated disagreement rate from running manual_rescore.py

\section{Limitations}
\label{sec:limitations}

This section enumerates the principal limitations of IPIBench V1. We report
them explicitly rather than eliding them, consistent with the responsible
disclosure norms of the security research community.

% ------------------------------------------------------------------
\subsection{Automated Scoring Is Heuristic-Based}
\label{sec:lim-scoring}
% ------------------------------------------------------------------

The automated pipeline uses a three-tier phrase-matching and signal-detection
scorer (\texttt{scoring\_v2.py}) that assigns each response a score of
$s \in \{0, 0.5, 1\}$ along with a confidence value $c \in [0,\,1]$.
While this extends the prior binary scheme and corrects three confirmed
systematic errors—a fabrication false negative (A003), a refusal-phrase
false positive (B010), and a partial-compliance misclassification (A033)—the
underlying mechanism remains heuristic.

To quantify residual error, we ran \texttt{manual\_rescore.py} against all
automated LLaMA 3.1 8B results and computed the disagreement rate between
automated and human binary judgements: \textbf{[X]\%}.
All rows with $c < 0.5$ were automatically flagged for manual review;
these flagged rows are excluded from the main results tables and reported
separately in the supplementary material.

Future work should replace the phrase-matching core with a fine-tuned
classifier trained on a human-annotated holdout set.

% ------------------------------------------------------------------
\subsection{Automated and Manual Evaluation Cohorts Are Not Comparable}
\label{sec:lim-cohorts}
% ------------------------------------------------------------------

Results for models evaluated via the automated API pipeline
(LLaMA 3.1 8B, LLaMA 3.3 70B, DeepSeek V3, and others)
are presented separately from results obtained through manual web-UI
testing (GPT-4.5, Claude 3.7 Sonnet).
These two cohorts differ on three dimensions:
(1)~evaluation surface (API vs.\ web interface),
(2)~system-prompt visibility (known vs.\ unknown), and
(3)~scoring method (automated three-tier vs.\ researcher binary judgement).
Direct cross-cohort ASR comparisons should not be drawn.

% ------------------------------------------------------------------
\subsection{Sample Size and Statistical Power}
\label{sec:lim-sample}
% ------------------------------------------------------------------

Each model is evaluated on 100 test cases across four defense modes
(400 observations per model). At this scale, the 95\% Wilson confidence
interval on a 50\% attack success rate is approximately
$\pm\,10$ percentage points, narrowing to $\pm\,5$pp at 20\% ASR.
All ASR figures in this paper are reported with their Wilson CIs;
readers should not over-interpret point estimates falling within
overlapping CIs.
McNemar's test is used for all paired defense-mode comparisons;
results marked as significant satisfy $p < 0.05$ after the
continuity correction described in \S\ref{sec:methodology}.

% ------------------------------------------------------------------
\subsection{Taxonomy Dimension Variance}
\label{sec:lim-taxonomy}
% ------------------------------------------------------------------

The IPIBench taxonomy encodes eight classification dimensions.
Four of these dimensions—\texttt{authority\_claimed},
\texttt{target\_action\_type}, \texttt{linguistic\_register}, and
\texttt{harm\_severity}—were generated by the migration script
(\texttt{migrate\_benchmark.py}) using narrow keyword heuristics and
exhibit low empirical variance: over 65\% of scenarios receive the
modal value in each dimension (see Appendix~\ref{app:taxonomy-variance}).
Consequently, these four dimensions are retained in \texttt{benchmark\_v2.json}
for metadata and filtering purposes but are \emph{excluded} from the
primary statistical analysis.
All paper figures and tables use only the four high-variance dimensions:
\texttt{category}, \texttt{attack\_goal}, \texttt{evasion\_style}, and
\texttt{injection\_position}.

% ------------------------------------------------------------------
\subsection{Cross-Lingual Generalization}
\label{sec:lim-crosslingual}
% ------------------------------------------------------------------

The benchmark contains a limited number of foreign-language injection
scenarios (evasion style: \texttt{foreign\_language}).
Cross-lingual results should be interpreted as preliminary evidence
rather than a systematic evaluation across language families.
A full multilingual extension is planned for V2.

% ------------------------------------------------------------------
\subsection{Responsible Disclosure Status}
\label{sec:lim-disclosure}
% ------------------------------------------------------------------

Three findings reported in this paper involve potential security
vulnerabilities in production AI systems:
(i) Grok 4 full tool-schema exfiltration (NRF-003) — disclosed to
\texttt{security@x.ai} prior to submission;
(ii) DeepSeek V3 probabilistic system-prompt exfiltration (NRF-002) —
disclosed to DeepSeek security prior to submission;
(iii) a rendering-layer vulnerability (NRF-026) — under active
coordinated disclosure and excluded from this version of the paper
pending vendor response within the standard 90-day window.
All other findings in this paper are based on standardized
benchmark prompts and do not constitute novel vulnerability disclosures.
